---
title: "Figures & Tables in Quarto"
author: "Wei Shen Lim"
date: "`r Sys.Date()`" #use your computer's date
format:
  html:
    toc: true
    toc-depth: 3 #set what how many headings levels show up
    toc-location: right
    toc-title: "Table of Contents"
    code-fold: true #code hidden by default, with a toggle button
    code-summary: "Show code" #customize the button label
embed-resources: true
warning: false
message: false
code-overflow: wrap
knitr:
  opts_chunk:
    fig.path: "../Output/" #saves all figures into 'Output' folder, ../ to go up one directory from 'Scripts', then to 'Output'
---

### **Load Libraries**

```{r}
library(tidyverse)
library(here)
library(kableExtra)
```

### **Load Data**

Using the same biogeochemistry dataset from *Silbiger et al. 2020* from Week 4.

```{r}
ChemData <- read_csv(here("Week_06", "Data", "chemicaldata_maunalua.csv"))
```

### **Prep Data**

I am removing all NAs and separating Tide_time column into two.

```{r}
ChemData_clean <- ChemData |> 
  drop_na() |> #remove all NAs
  separate_wider_delim(cols = Tide_time, #separate Tide_time column into appropriate columns
                       delim = "_",
                       names = c("Tide", "Time"),
                       cols_remove = FALSE)
```

### **Making a table**

Calculated mean, maximum, and minimum values for %SGD and salinity by:

- site
- season
- time
- tide

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary statistics of %SGD and salinity by site, season, time, and tide"

ChemData_clean |>
  group_by(Site, Season, Time, Tide) |> #group by these categories for summary statistics
  summarise(SGD_Mean = mean(percent_sgd, na.rm = TRUE), #calculate these summary statistics
            "SGD Max" = max(percent_sgd, na.rm = TRUE),
            "SGD Min" = min(percent_sgd, na.rm = TRUE),
            "Salinity Mean" = mean(Salinity, na.rm = TRUE),
            "Salinity Max" = max(Salinity, na.rm = TRUE),
            "Salinity Min" = min(Salinity, na.rm = TRUE)) |> 
  kbl(digits = 2) |> #make it a kable table
  kable_classic() |> #add a theme
  kable_styling(full_width = FALSE) #don't make it so wide
```

### **Making a figure**

Plotted the correlation between %SGD and salinity by season and time.

```{r}
#| label: fig-correlation-plot
#| fig-cap: "Correlation between %SGD and salinity by site and tide."
#| fig-align: "center" #center aligns the figure

ChemData_clean |> 
  ggplot(aes(x = percent_sgd, #correlation between percent_sgd & salinity
             y = Salinity,
             color = Tide)) +
  geom_smooth(method = "lm") + #best fit line
  geom_point(size = 2) + #scatter plot
  facet_wrap(~Site, ncol = 2) + #facet wrap by season
  theme_bw() + #bw theme to keep in clean but still have the grid lines
  theme(plot.title = element_text(size = 17), #change size of different text elements
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        strip.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12)) +
  labs(title = "Correlation between %SGD and salinity",
       x = "Submarine Groundwater Discharge (%)",
       y = "Salinity (ppt)",
       color = "Tide")
```

### **Final Conclusion**
As shown in @tbl-summary, the mean values of %SGD are consistently **higher** during low tide, while the mean values of salinity are consistently **lower** during low tide. This pattern between high and low tides, and the **negative correlation** between %SGD and salinity is further highlighted in @fig-correlation-plot. This suggests that salinity can be a good proxy for estimating percent SGD.