---
title: "Introduction to Quarto"
author: "Wei Shen Lim"
date: "`r Sys.Date()`" #use your computer's date
format: html
embed-resources: true
warning: false
message: false
code-overflow: wrap
---

```{r}
library(palmerpenguins)
library(tidyverse)
library(here)
library(beepr) #make beeping sound at the end of your code so you know it's done! #add beep(any number) at the end of your code
```

###### This part is testing how you can pull numbers directly from your dataset in R, rather than typing them manually, especially if dataset changes overtime.

```{r}
#| eval: false #don't run this chunk

`r nrow(penguins)` #count number of rows in the 'penguins' dataset

`r ncol(penguins)` #count number of columns in the 'penguins' dataset

`n_distinct(penguins$species)` #count number of different species in the species column, can do the same with other columns

`r round(mean(penguins$bill_length_mm, na.rm = TRUE))` #calculate the mean of bill length, while ommitting NA, and rounding the final value, can do the same with max(), min(), etc.
```

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.\
There are `r nrow(penguins)` penguins from `r n_distinct(penguins$species)` total species across `r n_distinct(penguins$island)` islands.\
The average bill length across all penguins is `r round(mean(penguins$bill_length_mm, na.rm = TRUE))`, with a maximum length of `r round(max(penguins$bill_length_mm, na.rm = TRUE))` and a minmum length of `r round(min(penguins$bill_length_mm, na.rm = TRUE))`.