---
title: "Quarto Part 2"
author: "Wei Shen Lim"
date: "`r Sys.Date()`" #use your computer's date
format:
  html:
    toc: true
    toc-depth: 3 #set what how many headings levels show up
    toc-location: right
    toc-title: "Table of Contents"
    code-fold: true #code hidden by default, with a toggle button
    code-summary: "Show code" #customize the button label
embed-resources: true
warning: false
message: false
code-overflow: wrap
knitr:
  opts_chunk:
    fig.path: "../Output/" #saves all figures into 'Output' folder, ../ to go up one directory from 'Scripts', then to 'Output'
---

```{r}
library(palmerpenguins)
library(tidyverse)
library(kableExtra)
library(memer) #make a meme in R!
```

### Simple plot with the penguins dataset
##### Change the size & position of the figure
##### Add labels and captions
```{r}
#| out-width: "70%" #makes it 70% of the width
#| fig-align: "center" #center aligns the figure
#| label: fig-penguin #label figures with fig- to reference later on
#| fig-cap: "Bill depth and length of Adelie, Chinstrap, and Gentoo Penguins"

ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     color = species)) +
  geom_point() +
  labs(title = "Bill depth and length",
       subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
       x = "Bill depth (mm)",
       y = "Bill length (mm)",
       color = "Species",
       caption = "Source: Palmer Station LTER / palmerpenguins package") +
  scale_color_viridis_d()
```

### Make tables with kabelExtra
##### Add some style
```{r}
#| label: tbl-penguin-means #label tables with tbl- to reference later on
#| tbl-cap: "Mean bill length by species."

penguins |> 
  group_by(species) |> 
  summarise(billmean = mean(bill_length_mm, na.rm = TRUE)) |> 
  kbl() |> #make it a kable table
  kable_classic() |> #add a theme
  row_spec(2, bold = TRUE, color = "white", background = "red") |> #highlight row 2
  kable_styling(full_width = FALSE) #don't make it so wide
```

### Cross-refereces: Figures
```{r}
#reference figures by typing @ followed by the label name of the figure, ex: @fig-penguin
#it's automatically numbered, i.e. shown as "Figure 1"
```

As shown in @fig-penguin, bill depth and bill length are positively correlated across all 3 species.

### Cross-refereces: Tables
```{r}
#same thing with tables, ex: @tbl-penguin-means
#also automatically numbered, i.e. shown as "Table 1"
```

Mean bill lengths are summarised in @tbl-penguin-means.

### Today's totally awesome R package (Meme!)
```{r}
meme_get("DistractedBf") |> 
  meme_text_distbf("Silly R package", "OCN 682 students", "actual coding")
```

